### 2020-06-19 README.Rmd
news update

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/antaldaniel/eurobarometer/branch/master/graph/badge.svg)](https://codecov.io/gh/antaldaniel/eurobarometer?branch=master)
[![Project Status: Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
"[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)"
"[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/eurobarometer)](https://cran.r-project.org/package=eurobarometer)"
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3825700.svg)](https://doi.org/10.5281/zenodo.3825700)
[![Follow author](https://img.shields.io/twitter/follow/antaldaniel.svg?style=social)](https://twitter.com/intent/follow?screen_name=antaldaniel)

[![Travis build status](https://travis-ci.com/antaldaniel/eurobarometer.svg?branch=master)](https://travis-ci.com/antaldaniel/eurobarometer)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/antaldaniel/eurobarometer.svg?branch=master)](https://travis-ci.com/antaldaniel/eurobarometer)
[![Codecov test coverage](https://codecov.io/gh/antaldaniel/eurobarometer/branch/master/graph/badge.svg)](https://codecov.io/gh/antaldaniel/eurobarometer?branch=master)
[![Project Status: Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
"[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)"
"[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/eurobarometer)](https://cran.r-project.org/package=eurobarometer)"
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3825700.svg)](https://doi.org/10.5281/zenodo.3825700)
[![Follow author](https://img.shields.io/twitter/follow/antaldaniel.svg?style=social)](https://twitter.com/intent/follow?screen_name=antaldaniel)
[![Follow contributor](https://img.shields.io/twitter/follow/martakolcz.svg?style=social)](https://twitter.com/martakolcz?lang=en)

<!-- badges: end -->
